 % LaTeX Curriculum Vitae Template

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{sectsty}

\sectionfont{\fontsize{12}{15}\selectfont}

% Set your name here
\def\name{Jesse Franklin}


% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\name},
	pdfkeywords = {economics, statistics, mathematics},
	pdftitle = {\name: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\geometry{
	body={6.5in, 8.5in},
	left=0.5in,
	right=0.5in,
	top=1in,
	bottom=1in
}

\usepackage{fancyhdr}
\fancypagestyle{firststyle}
{
	\fancyhf{}
	\chead{Jesse Franklin} 
	\rhead{\href{mailto:jfranklin1185@gmail.com}{jfranklin1185@gmail.com}\\303-330-1185}
	\lhead{\url{https://jefranko.github.io/}}
}

\begin{document}
	\thispagestyle{firststyle}
	\section*{Education}
	
	\noindent International Baccalaureate High School Degree, Summa Cum Laude, $2016.$\\
	
	\noindent B.A. Mathematics, University of Colorado Boulder, Magna Cum Laude $2019.$\\
	
	\noindent Ph.D. Mathematics, University of Vermont, May $2024.$ 
	
	\section*{Employment}
	\noindent Salt Lake Community College --- Adjunct Faculty (Fall $2024$, Spring $2025$):\\
	\textit{(Introduction to Statistics; College Algebra; Quantitative Reasoning; Business Precalculus)}\\
	
	\noindent Lumos Solar --- SEO Manager (Current).\\
	
	\noindent University of Vermont --- Graduate Teaching Assistant ($2019-2024$):\\
	\textit{Five years of instruction including syllabus/course planning, all lecturing and creation of exams. (Calc $1,$ Precalc and Applications of Finite Math courses)}
	%\begin{enumerate}
	%\item[] University of Vermont --- Graduate Teaching Assistant (ongoing):\\
	%	\textit{Five years of instruction of courses for non-math majors, including syllabus/course planning, all lecturing and creation of exams.}\\
	%%\item[] Southwest Research Institute - Data Analyst Intern (Summer $2016$): \\
	%%	\textit{Thermal Vaccum Test, Data Analysis, Programming in Python, and Ruggidization of Suborbital Flight Instrument for Solar Imaging} 
	%%\item[] Lumos Solar - Warehouse Supervisor (Summer $2017$): \\
	%%	\textit{Helping the family buisness by organizing new warehouse including shipping and receiving}
	%%\item[] CorePower Yoga - Instructor ($2018-2019$):\\
	%%	\textit{Teaching Yoga}
	%\end{enumerate}
	
	\section*{Papers}

	%\noindent (BA Honors Thesis) Independent Study: Representation Theory and Combinatorial Methods (May $2018$-May $2019$)
	\noindent (preprint) The Geometry of Drinfeld Modular Forms --- \href{https://arxiv.org/abs/2310.19623}{arXiv: $2310.19623$}. Under review at Journal of Number Theory.\\
	
	\noindent (preprint) Section Rings of $\mathbb{Q}$-divisors on Genus $1$ Curves --- \href{https://arxiv.org/abs/2312.15128}{arXiv: $2312.15128$} --- Joint work with Evan O'Dorney and Michael Cerchia. Under review at Algebra and Number Theory.\\
	
	\noindent (Thesis) Computing the Canonical Ring of Certain Stacks. Available Upon Request.\\
	
	\noindent (preprint) On Drinfeld modular curves for SL$(2)$ --- \href{https://arxiv.org/abs/2408.00198#}{arXiv:$2408.00198$} --- Joint work with Mihran Papikian and Sheng-Yang Kevin Ho. Under review at International Journal of Mathematics.

	
	\section*{Academic Awards}
	In both May $2023$ and May $2024$ I received the John F.\ Kenney award for ``Excellence in Mathematics'' from the University of Vermont. 
	
	\section*{References/Advisors}
	\noindent Dr.\ Christelle Vincent, Assistant Professor University of Vermont. \href{mailto:christelle.vincent@uvm.edu}{christelle.vincent@uvm.edu}\\
	\noindent Dr.\ Taylor Dupuy, Associate Professor University of Vermont. \href{mailto:taylor.dupuy@uvm.edu}{taylor.dupuy@uvm.edu}\\
	%\noindent Dr.\ Nat Thiem, Associate Professor University of Colorado at Boulder.  \href{mailto:nathaniel.thiem@colorado.edu}{nathaniel.thiem@colorado.edu}\\
	\noindent Dr.\ John Voight, Professor of Mathematics, University of Sydney.
	\href{mailto:jvoight@gmail.com}{jvoight@gmail.com}\\
	\noindent Ron McKay, Dean of Mathematics, Salt Lake Community College. \href{mailto:ronald.mckay@slcc.edu}{ronald.mckay@slcc.edu}
	
	\section*{Conferences/Seminars}
	\noindent University of Vermont Algebraic Number Theory seminar (unQVNTS) --- organizer for $2022$-$2024$\\
		%\noindent Arizona Winter School $2020$ --- participant
		%\noindent Algebraic Geometry in the time of Covid (AGittoC) --- participant
		%\noindent Upstate NY Number Theory at Union College $2021$ --- participant
		%\noindent Connecticut Summer School in Number Theory (CTNT) $2022$ --- participant
	\noindent Park City Mathematics Institute (PCMI); $2022$ --- Teaching Assistant to the Undergraduate Summer School Program on Cryptography\\
	\noindent Explicit Computations with Stacks AMS MRC; June $2023$ --- Participant\\
	\noindent AGNES @UPenn; October $2023$ --- Poster\\
	\noindent Dartmouth-UVM Math Day; February $2024$ --- Contributed Talk\\
	\noindent University of Utah Number Theory/Representation Theory Seminar; November $2024$ - Invited speaker
	
	
	
	
\end{document}
